Automatic Summarization of Scientific Texts

### 2018-06-10 paper/paper.tex
Updated the related work

Allahyari et al.\cite{allahyari-17} make a survey of the most successful text summarization techniques as of July 2017.

This September Li et al. \cite{li-cohn-17} described their submission to the sentiment analysis sub-task of ?Build It, Break It: The Language Edition (BIBI)? where they successfully apply generative approach to the problem of sentiment analysis.

In their paper \textit{Generative Adversarial Network for Abstractive Text Summarization} Liu et al.\cite{liu-17} built an adversarial model that achieved competitive ROUGE scores with the state-of-the-art methods on CNN/Daily Mail dataset. They compare the performance of their approach with three methods, including the abstractive model, the pointer-generator coverage networks, and the abstractive deep reinforced model.

In contrast Zhang et al.\cite{zhang-17} don't use reinforcement learning but rather introduce TextGAN with an LSTM-based generator and kernelized discrepancy metric.

@@

\subsection{Machine learning approach}

@@

However, in their latest paper Fedus, Goodfellow, and Dai\cite{fedus-18} overcome this problem by using reinforcement learning to train the generator while the discriminator is still trained via maximum likelihood and stochastic gradient descent, and use it to fill the gaps in the text.

@@

Rapid Automatic Keyword Extraction algorithm (RAKE)\cite{rose-10} is a keyword extraction algorithm which tries to determine key phrases in a body of text by analyzing the frequency of word appearance and its co-occurance with other words in the text. Its main advantages include  time efﬁciency, operating on individual documents. It can be easily applied to new domains and multiple types of documents. RAKE is very sensitive to unclean data, as it relies on word frequency.

@@

\section{Evaluating results}

@@

\begin{table}[H]
\caption{Evaluating different models with ROUGE}

\begin{center}
\begin{tabular}{|l|c|c|c|c|}
\hline
\textbf{Model} & \textbf{ROUGE-1} & \textbf{ROUGE-2} & \textbf{CAROUGE-1} \\
\hline
TextRank & 0.18 & 0.04 & 0.89 \\
RAKE & 0.08 & 0.02 & 0.82 \\
\hline
\end{tabular}
\end{center}
\end{table}

@@

\begin{table}[H]
\caption{Evaluating different models with ROUGE}

\begin{center}
\begin{tabular}{|l|c|c|c|c|}
\hline
\textbf{Model} & \textbf{ROUGE-1} & \textbf{ROUGE-2} & \textbf{CAROUGE-1} \\
\hline
Human & 0.77 & 0.43 & 0 \\
\hline
\end{tabular}
\end{center}
\end{table}

@@

>>>>

Das et al. made a survey of the most successful text summarization techniques as of the year 2007\cite{das-7}. Simmilar survey was made 10 years later by Allahyari et al\cite{allahyari-17}.

ROUGE - the most widely used metric for text summarization was presented by Chin-Yew Lin in July 2004\cite{lin-4}. The metric developed by us is greatly influenced by the the work of this author. Great overview of existing evaluation metrics was also done in \cite{das-7} and \cite{allahyari-17}.

Fedus, Goodfellow, and Dai\cite{fedus-18} wrote an amazing paper about their application of generative adversarial networks to the problem of filling the gaps in text. However, as we show in section \ref{sec:ml}, this approach can not be easily applied to our problem.

@@

\subsection{Machine learning approach}
\label{sec:ml}

@@

However, in their latest paper Fedus, Goodfellow, and Dai\cite{fedus-18} overcome this problem by using reinforcement learning to train the generator while the discriminator is still trained via maximum likelihood and stochastic gradient descent, and use it to fill the gaps in the text. This is an amazing result that can become an inspiration for others to develop GAN-based solutions for the problems of text sumarization. Nevertheless, summarization is way more complex than the problem of filling the gaps, and therefore, to our knowledge, there are no successful examples of applying adversarial networs to problems similar to ours. We ourselves have tried this new approach, but failed to produce good results.

@@

Rapid Automatic Keyword Extraction algorithm (RAKE)\cite{rose-10} is a keyword extraction algorithm which tries to determine key phrases in a body of text by analyzing the frequency of word appearance and its co-occurance with other words in the text. Its main advantages include time efficiency, operating on individual documents. It can be easily applied to new domains and multiple types of documents. RAKE is very sensitive to unclean data, as it relies on word frequency.

@@

\section{Evaluating results}
\label{sec:results}

@@

\begin{table}[H]
\caption{Evaluating summarization algorithms}

\begin{center}
\begin{tabular}{|l|c|c|c|c|}
\hline
\textbf{Model} & \textbf{ROUGE-1} & \textbf{ROUGE-2} & \textbf{CAROUGE-1} \\
\hline
RAKE & 0.08 & 0.02 & 0.82 \\
TextRank & 0.18 & 0.04 & 0.89 \\
\hline
\end{tabular}
\end{center}
\end{table}

@@

\begin{table}[H]
\caption{Evaluating human judges}

\begin{center}
\begin{tabular}{|l|c|c|c|c|}
\hline
\textbf{Model} & \textbf{ROUGE-1} & \textbf{ROUGE-2} & \textbf{CAROUGE-1} \\
\hline
Human & 0.77 & 0.43 & 0.98 \\
\hline
\end{tabular}
\end{center}
\end{table}

@@

As we have seen in section \ref{sec:results}, both ROUGE and CAROUGE metrics give very high scores to human-created summaries, and much lower scores for the summaries produced by algorithms. However, consider the fact that the base assumption of ROUGE takes human judgement as the ground truth
